Syntactically Informed Natural Language Inference

### 2019-03-22 cse517/report/main.tex
Minor spelling/syntax changes.

We extend the decomposable attention (DA) model by \citet{Parikh2016-em}
incorporating syntactic features.
The DA model obtained state-of-the-art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.
We primarily
evaluate on the domain-specific SciTail dataset \citep{Khot2018-th}
for both its smaller size and lack of annotation artifacts when compared to SNLI
\citep{Gururangan2018-lj}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/da-h2p-attention.png}
    \caption{Hypothesis to premise attention weights of the DA model when processing
             the input from tabel~\ref{table:example}.}
    \label{fig:da-attention-weights}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/syntail-h2p-attention.png}
    \caption{Hypothesis to premise attention weights of syntail v1 when processing
             the input from tabel~\ref{table:example}.}
    \label{fig:sytail-attention-weights}
\end{figure}

@@

Other works have experimented with incorporating syntactic learning objectives.
\citet{Strubell2018-qw} achieved state-of-the-art performance
for a model using predicted predicates and standard word embeddings on
CoNLL-2005 SRL by performing multi-task training on additional syntactic tasks.
\citet{Swayamdipta2017-ct} use hard-coded constituency and dependency parse features
and a syntactic scaffold to
extend softmax margin segmental RNN (segRNN) model.

>>>>

We extend the decomposable attention (DA) model from  \citet{Parikh2016-em} by
incorporating syntactic features.
The DA model obtained state-of-the-art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.
We primarily
evaluate on the domain-specific SciTail dataset \citep{Khot2018-th}
for both its smaller size and lack of annotation artifacts when compared to SNLI
\citep{Gururangan2018-lj}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/da-h2p-attention.png}
    \caption{Hypothesis to premise attention weights of the DA model when processing
             the input from table~\ref{table:example}.}
    \label{fig:da-attention-weights}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/syntail-h2p-attention.png}
    \caption{Hypothesis to premise attention weights of syntail v1 when processing
             the input from table~\ref{table:example}.}
    \label{fig:sytail-attention-weights}
\end{figure}

@@

Other works have experimented with incorporating syntactic learning objectives.
\citet{Strubell2018-qw} achieved state-of-the-art performance
for a model using predicted predicates and standard word embeddings on
CoNLL-2005 SRL by performing multi-task training on additional syntactic tasks.
\citet{Swayamdipta2017-ct} use hard-coded constituency and dependency parse features
and a syntactic scaffold to
extend the softmax margin segmental RNN (segRNN) model.
